Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-22 draft/ms_v4.tex
More edits from Alexie

    Next, we identify stars that are misidentified by \hscpipe{} as extended
    objects using the \texttt{classification.extendedness} parameter in each band.
    The fraction of misclassification is ${\sim}8$--$15$\%, and clearly depends on
    seeing conditions.
    For the same reason, $g$-band has the highest fraction of misclassification,
    while $i$-band is recommended for selecting point sources.
    The misclassified stars are on average ${\sim}1$ mag fainter than the others \alexie{xx}.
    We exclude them from the photometric comparison below, and further discuss
    the star--galaxy separation issue in Section \ref{ssec:sg}.

@@

\alexie{TO HERE}

We define the  \s2n{} for PSF photometry as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band
    without considering aperture corrections.
    This helps us visualize
    1) the detection limit for point sources,
    2) the impact of seeing condition on PSF photometric,
    3) and the scatter of photometric accuracies at a fixed input magnitude given all
       the realistic features of HSC images (e.g., background subtraction, nearby
       objects, optical artifacts).
    We show the results for $g$- and $i$-bands in Fig \ref{fig:star_sn}, and find close
    relations in both bands.

    As expected, we clearly see that the seeing condition impacts the \s2n{} of point
    sources at fixed input magnitude.
    In  $i$-band, the bad-seeing (0.7\asec{}) \tract{}  shows systematically
    lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
     \s2n{} is similar for the two $g$-band \tracts{} because they share similar seeing conditions.
    Our results show that blendedness can also affect the accuracy of PSF photometry.
    In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
    fixed magnitude.
    Interestingly, the effect is not obvious in $g$-band, suggesting the deblending
    process and photometric quality of blended objects also depend on seeing condition.

@@

\subsubsection{Accuracy of PSF magnitude}

    Now, we look into PSF magnitude accuracy in each of the five bands
    independently.
    Fig \ref{fig:psf_mag} shows the relation between the input magnitude and the
    magnitude difference from the \hscpipe{} \forced{} PSF photometry.

    The overall performance of PSF photometry is excellent.
    In $i$-band, the median magnitude difference for \tract{} with 0.45\asec{} seeing is
     ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
    $i_{\mathrm{Input}}{\sim}19.0$ mag.
    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF
    magnitude holds at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
    ${\sim}7$\% level with an average ${\sim}0.072$ mag difference.
    The bad-seeing \tract{} shows similar accuracy of PSF photometry at
    $i_{\mathrm{Input}}<23.5$ mag.
    At the faint end, the accuracy becomes slightly worse: ${\sim}5$\% accuracy around
    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% accuracy around
    $i_{\mathrm{Input}}{\sim}25.2$ mag.
    \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
    which is consistent with our results.
    At fainter magnitude, external comparisons become difficult due to the lack of deep
    imaging data at HSC level and also due to the impact of the color-term when comparing photometry
    using different filters.
    The results from \synpipe{} hence provide more useful evaluations down to the
    detection limit\footnote{Strictly speaking, the uncertainties here should be
    considered as the lower limit because \synpipe{} currently does not consider the uncertainties
    in PSF modeling.}.

    We also see that the accuracy of PSF photometry does not strongly depend on filters.
    The accuracy of the forced PSF magnitude in $r$- and $z$-bands is similar to
    $i$-band observations (1.5-4.0\% at $19.0 < r_{\mathrm{Input}} < 24.0$ mag, ${\sim}8$\% down to
    $r_{\mathrm{Input}}{\sim}25.2$ mag;
    1.0-5.0\% at $19.0 < z_{\mathrm{Input}} < 24.0$ mag, ${\sim}10$\% down to
    $z_{\mathrm{Input}}{\sim}25.2$ mag).
    The accuracies in $g$- and $y$-bands become slightly worse (1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
    $g_{\mathrm{Input}}{\sim}25.2$ mag;
    1.5-5.0\% at $19.0 < y_{\mathrm{Input}} < 23.0$ mag, ${\sim}12$\% down to
    $y_{\mathrm{Input}}{\sim}24.0$ mag;); however, the differences can be attributed to the
    differences in seeing conditions.

    For relatively isolated stars, \hscpipe{} provides unbiased PSF photometry down to a
    very faint magnitude in $i$- and $z$-bands.
    For $g$-, $r$-, and $y$-bands, we find small offsets in the distributions of magnitude
    differences, which indicates \hscpipe{} tends to underestimate the fluxes of stars
    in these bands by ${\sim}0.01-0.02$ mag.
    Although the exact cause of this offset is unclear (it could be related to
    differences in seeing), it will not affect the accuracies of magnitudes or colors.

    At the same time, the story for highly blended stars is very different.
    \hscpipe{} on average systematically underestimates their total fluxes by
    $0.05$--$0.10$ mag at a fixed input magnitude.
    We see the same effect in all bands, and the impact of blendedness becomes
    increasingly significant at fainter magnitude.
    It is important to keep this in mind when using PSF photometry for point
    sources in HSC data.

    We also test the \unforced{} PSF photometry in all five bands, and find very similar
    accuracies.
    While measuring \forced{} PSF photometry, \hscpipe{} fixes the centroid
    of the PSF model across all five bands.
    Therefore, the  difference between \forced{} and \unforced{} PSF magnitudes
    indicates the photometric uncertainties induced by the differences in the accuracies of
    astrometric calibrations and PSF modeling among different bands.
    We highlight the differences between \forced{} and \unforced{} PSF photometry of
    $g$- and $y$-bands in Fig \ref{fig:psf_diff}.
    The overall difference is very small ($<0.01$ mag), but it also suggests that
    \hscpipe{} \unforced{} PSF photometry systematically recovers slightly more fluxes
    at the very faint end.

\subsubsection{Accuracy of the PSF colors}

>>>>

    Next, we exclude stars that are misidentified by \hscpipe{} as extended
    objects using the \texttt{classification.extendedness} parameter in each band.
    The fraction of misclassification is ${\sim}10$--$20$\%, and clearly depends on
    seeing conditions.
    For the same reason, $g$-band has the highest fraction of misclassification,
    while $i$-band is recommended for selecting point sources.
    The star--galaxy separation issue is discussed more in Section \ref{ssec:sg}.

@@

The \s2n{} for PSF photometry is defined as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band (no aperture corrections) \alexie{have you defined aperture correction?}. Figure  \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} in the $g$- and $i$-bands. This Figure  shows the expected  \s2n{} of stars as a function of magnitude for the Wide layer.

%    This helps us visualize
%    1) the detection limit for point sources,
%    2) the impact of seeing condition on PSF photometric,
%    3) and the scatter of photometric accuracies at a fixed input magnitude given all
%       the realistic features of HSC images (e.g., background subtraction, nearby
%       objects, optical artifacts). \alexie{Why is this relevant in this figure? I wouldn't use SN to quantofy this?}

    Figure \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
    sources at fixed input magnitude.
    In  $i$-band, the bad-seeing (0.7\asec{}) \tract{}  shows systematically
    lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
     The \s2n{} is similar for the two $g$-band \tracts{} because they share similar seeing conditions. 
    %Our results show that blendedness can also affect the accuracy of PSF photometry.\alexie{why use SN here?}
    %In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
    %fixed magnitude.
    %Interestingly, the effect is not obvious in $g$-band, suggesting the deblending
    %process and photometric quality of blended objects also depend on seeing condition.

@@

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Accuracy of PSF magnitudes}

    We now investigate the accuracy of the PSF magnitude in each of the five bands
    independently. Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the  \hscpipe{} \forced{} PSF magnitude as a function of input magnitude.

    The overall performance of the \hscpipe{} \forced{} PSF magnitude is excellent. The median $i$-band magnitude difference for the \tract{} with 0.45\asec{} seeing is
     ${\sim}0.015$ mag (${\sim}1.5$\%) at
    $i_{\mathrm{Input}}{\sim}19.0$ mag. At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of the PSF
    magnitude is ${\sim}3$\% level (${\sim}0.036$ mag average difference).
    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
    ${\sim}7$\% with an average ${\sim}0.072$ mag difference.

    The accuracy of the PSF photometry for the bad-seeing \tract{} shows a similar performance at  $i_{\mathrm{Input}}<23.5$ mag. At fainter magnitudes, the accuracy slightly degrades. The bad-seeing \tract{} displays a performance of ${\sim}5$\% accuracy at
    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% accuracy at
    $i_{\mathrm{Input}}{\sim}25.2$ mag.
    \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
    which is consistent with our results. At fainter magnitudes however, external comparisons become difficult due to the  lack of imaging matched to HSC depths.
    The results from \synpipe{} hence provide  useful evaluations of  the accuracy of the HSC photometry  down to our detection limit\footnote{Strictly speaking, the uncertainties reported here should be
    considered as the lower limit because \synpipe{} currently does not consider PSF modeling uncertainties}.

Figure \ref{fig:psf_mag} also shows that the accuracy of the PSF photometry is not filter dependent. The accuracy of forced PSF magnitudes in $r$ and $z$ is similar to the $i$-band. For $r$ band we find  1.5-4.0\% at $r_{\mathrm{Input}} < 24.0$ and ${\sim}8$\% at $r_{\mathrm{Input}}{\sim}25.2$. For $z$-band we find  \alexie{xxxxx reformat}

 1.0-5.0\% at $19.0 < z_{\mathrm{Input}} < 24.0$ mag, ${\sim}10$\% down to
    $z_{\mathrm{Input}}{\sim}25.2$ mag).

    The accuracy in the $g$ and $y$-bands becomes slightly worse (1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
    $g_{\mathrm{Input}}{\sim}25.2$ mag;
    1.5-5.0\% at $19.0 < y_{\mathrm{Input}} < 23.0$ mag, ${\sim}12$\% down to
    $y_{\mathrm{Input}}{\sim}24.0$ mag;). These differences are however consistent with the differences in the seeing conditions between the filters

The PSF photometry for relatively isolated stars is unbiased in the $i$- and $z$-bands down to faint magnitudes . For the $g$, $r$, and $y$-bands, we find small offsets between the  input and recovered magnitude. \hscpipe{} tends to underestimate the fluxes of stars
    in these bands by ${\sim}0.01-0.02$ mag. The exact cause of this offset is unclear but the levels of bias is quite small and not a major concern.

	However, Figure \ref{fig:psf_mag} also shows that blending has a strong impact on photometry estimation.  On average, \hscpipe{} on average systematically underestimates the total fluxes of stars that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input magnitude.
    We see the same effect in all bands, and the impact of blendedness becomes
    increasingly significant at fainter magnitudes.
    It is important to bear this caveat in mind when using PSF photometry for point
    sources in HSC data.

	Finally, we also perform similar tests for the \unforced{} PSF photometry in all five bands, and find similar results.  To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid
    of the PSF model across all five bands. A difference between \forced{} and \unforced{} PSF magnitudes would therefore be an indication of  photometric uncertainties  arising from  inaccurate astrometric calibrations and PSF modeling across different bands. Figure  \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} PSF photometry for the $g$ and the $y$ band. The overall differences are small ($<0.01$ mag) .

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Accuracy of PSF colors}

\alexie{ALEXIE EDITED TO HERE}
